Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-01-21 paperIEEE.tex
Graphs up to date
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@93 db7c848b-7755-4df2-b763-8796797afa52
Describe tree_equalizer
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@94 db7c848b-7755-4df2-b763-8796797afa52

\subsubsection{Sort-First and Sort-Last Load Equalizer}

Sort-first (\fig{fig:loadeq}) and sort-last load balancing is the most obvious
optimization for these parallel rendering modes. Our load equalizer is fully
transparent for application developers; that is, it uses a reactive approach
based on past rendering times. This assumes a reasonable frame-to-frame
coherency. Our implementation stores a 2D or 1D grid of the load, mapping the
load of each channel. The load is stored in normalized 2D/1D coordinates using
$\frac{time}{area}$ as the load, the contributing source channels are organized
in a binary tree, and then the algorithm balances the two branches of each level
by equalizing the integral over the area on each side. We have implemented
various tunable parameters allowing application developers to optimize the load
balancing based on the characteristics of their rendering algorithm:

>>>>

\subsubsection{Sort-First and Sort-Last Load Balancing}

Sort-first (\fig{fig:loadeq}) and sort-last load balancing are the most obvious
optimizations for these parallel rendering modes. Our load equalizers are fully
transparent for application developers; that is, they use a reactive approach
based on past rendering times. This assumes a reasonable frame-to-frame
coherency. Equalizer implements two different algorithms, a
\textsf{load\_equalizer} and a \textsf{tree\_equalizer}. The result section
provides some evidence on the strengths and weaknesses of both algorithms.

The \textsf{load\_equalizer} stores a 2D or 1D grid of the load, mapping the
load of each channel. The load is stored in normalized 2D/1D coordinates using
$\frac{time}{area}$ as the load, the contributing source channels are organized
in a binary tree, and then the algorithm balances the two branches of each level
by equalizing the integral over the cost area map on each side.

The \textsf{tree\_equalizer} also uses a binary tree for recursive load
balancing. It computes the accumulated render time on all nodes of the tree, and
uses this to allocate an equal render time to each subtree. It makes no
assumption of the load distribution in 2D or 1D space, it only tries to correct
the imbalance in render time.

We have implemented various tunable parameters for both equalizers allowing
application developers to optimize the load balancing based on the
characteristics of their rendering algorithm:
